### 2014-11-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Completed Test Tables

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Fuel masses}
	\begin{tabular}{llcc}
		\hline\noalign{\smallskip}
		Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
		%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
		%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
		%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
		% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
		%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
		%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
		3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
		2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
		3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
		Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
		2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
		2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
		3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
		3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
		3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
		Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
		3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
		Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}

>>>>

\subsection{Uncertainty}
\label{subsec:Uncertainty}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Fuel masses}
	\begin{tabular}{llcc}
		\hline\noalign{\smallskip}
		Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
		Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
		Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
		Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
		2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
		Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
		Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
		3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
		2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
		3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
		Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
		2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
		2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
		3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
		3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
		3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
		Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
		3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
		Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fuel_Masses}
\end{sidewaystable}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Test Descriptions}
	\begin{tabular}{lllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Flow Rate			& Comments \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		2 (FSW2)   	& Water     &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120 gpm    		&	Furniture Fuel Package	\\
		5 (FSE5)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		6 (FSW6)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		7 (FSW7)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
		8 (FSE8)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		9 (Attic 1) &  Water    &  Straight Stream  	&  120 gpm    		&	Furniture Fuel Package	\\
		10 (Attic 2)&  CAF      &  Straight Stream  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
		11 (FSE1)   &  Water    &  30 deg Fog  			&  120 gpm   		&	Wood Fuel Package, Panel Window	 \\
		12 (FSW1)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
		13 (FSE2)   &  Water    &  30 deg Fog  			&  120 gpm    		&	Wood Fuel Package, Panel Window  \\
		14 (FSW2)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Test_Descriptions}
\end{sidewaystable}

\begin{sidewaystable}[!ht]
	\centering
	\caption{Nozzle Activation Times}
	\begin{tabular}{lllllll}
		\hline\noalign{\smallskip}
		Test		& Agent		& Stream				& Nozzle 1 Activation	& Nozzle 1 Shut Off		& Nozzle 2 Activation	& Nozzle 2 Shut Off \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 (FSE1)    &  CAF      &  30 deg Fog  	    	& 233 					& 248					& 269					& 284					\\
		2 (FSW2)   	& Water     &  30 deg Fog  	    	& 235					& 250					& 272					& 287					\\
		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore     & 228					& 243 					& 255					& 270					\\
		4 (FSE4)    &  Water    &  7/8" Smooth Bore     & 233					& 248					& 268					& 283					\\
		5 (FSE5)    &  Water    &  30 deg Fog  	    	& 232					& 247					& 257					& 272					\\
		6 (FSW6)    &  CAF      &  30 deg Fog     		& 239					& 254					& 268					& 283					\\
		7 (FSW7)    &  Water    &  30 deg Fog     		& 276					& 291					& 308					& 323					\\
		8 (FSE8)    &  CAF      &  30 deg Fog     		& 245					& 260					& 275					& 290					\\
		9 (Attic 1) &  Water    &  Straight Stream     	&						&						&						&					\\
		10 (Attic 2)&  CAF      &  Straight Stream     	& 						&						&						&					\\
		11 (FSE1)   &  Water    &  30 deg Fog  	   		& 315					& 330					& 345					& 360					\\
		12 (FSW1)   &  CAF      &  30 deg Fog  	   		& 233					& 248					& 263					& 278					\\
		13 (FSE2)   &  Water    &  30 deg Fog  	   		& 330					& 390					& 406					& 466					\\
		14 (FSW2)   &  CAF      &  30 deg Fog  	  		& 435					& 495					& 510					& 570					\\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Nozzle_Activation_Times}
\end{sidewaystable}
